Recovery of mountain plant communities in response to reductions in Nitrogen emissions is hidden by other drivers of global change

### 2018-06-14 Manuscript.Rmd
Claculation of pseudo-turnover between two survey from the same year.

Nitrogen deposition decreased with increasing elevation (\@ref(fig:Ndepchange)a). In 2010 only `r 100 * mean(sites$NTOT_2010 < 10)`% of sites had a Nitrogen deposition rate of less than 10 kg N ha$^{-1}$ yr$^{-1}$, which lied all above 1000m. Between 2000 and 2010 the Nitrogen deposition decreased in average around 2 kg N ha$^{-1}$ yr$^{-1}$ with slightly larger net decreases at lower elevation (\@ref(fig:Ndepchange)a).

>>>>

Nitrogen deposition decreased with increasing elevation (Fig. \@ref(fig:Ndepchange)a). In 2010 only `r 100 * mean(sites$NTOT_2010 < 10)`% of sites had a Nitrogen deposition rate of less than 10 kg N ha$^{-1}$ yr$^{-1}$, which lied all above 1000m. Between 2000 and 2010 the Nitrogen deposition decreased in average around 2 kg N ha$^{-1}$ yr$^{-1}$ with slightly larger net decreases at lower elevation (Fig. \@ref(fig:Ndepchange)a).
